---
title: "predicting memory performance"
author: "Adam Dede"
date: "2024-07-13"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Load packages and set up environment

```{r message = FALSE, warning = FALSE}

knitr::opts_chunk$set(message = FALSE, warning = FALSE)

# load packages
library(tidyverse)
library(RColorBrewer)
library(hrbrthemes)
library(lme4)
# library(lmerOut)
library(lmerTest)
library(car)
library(ggeffects)
library(emmeans)
library(effects)

# set contrasts
options(contrasts=c("contr.Sum","contr.Helmert"))
options(decorate.contr.Sum="",decorate.contrasts=c("[","]"))

```

## Read in data frame

```{r load data}

# load in main data frame
df <- read.csv("R:\\MSS\\Johnson_Lab\\dtf8829\\GitHub\\HpcAccConnectivityProject\\allSig.csv", header = T)


```

## reformat into better format

```{r demo stats}

longDF <- df %>% pivot_longer(cols = -all_of(c('subID', 'sex', 'age', 'memAcc', 
                                               'memD', 'reg', 'encHIT', 
                                               'encMISS', 'retHIT', 'retMISS')),
                              names_to = c('type', 'regionphase'), 
                              names_pattern = "^([^_]+)(.*)$",
                              values_to = 'stat'
                              ) %>%
          filter(!is.nan(stat))

longDF1 <- filter(longDF, type == 'ppc')
longDF2 <- filter(longDF, type != 'ppc')
longDF1$HFB = grepl('HFB', longDF1$regionphase)
longDF2$HFB = grepl('peak', longDF2$type)

longDF <- rbind(longDF1, longDF2)


longDF <- longDF %>% 
  filter(reg == "mtl" | reg == "hip" | reg == "acc" | 
         reg == "dlPFC" | reg == "pPFC")


test <- longDF %>% group_by(type, regionphase, HFB) %>%
  summarize(corVal = cor(memAcc, stat), 
            count = n()) 
test = test[test$count>8,]


df_hist <- test %>%
  group_by(HFB) %>%
  mutate(bin = cut(corVal, breaks = seq(-1,1,.2))) %>%  # You can adjust the number of breaks
  count(HFB, bin) %>%
  group_by(HFB) %>%
  mutate(proportion = n / sum(n))

# Plot the histogram with proportions
ggplot(df_hist, aes(x = bin, y = proportion, fill = HFB)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(y = "Proportion", x = "Value", title = "Histogram Scaled to Within-Group Proportion") +
  theme_minimal() +
  facet_wrap(~ group, scales = "free_x")



test %>% ggplot(aes(x = corVal, color = HFB, fill = HFB)) + 
  geom_histogram(aes(y = ..density..), bins = 10)+
  scale_y_continuous(labels = scales::percent_format()) 



age.lm = lm(age ~ as.factor(reg), data = df)
summary(age.lm)

sex.glm = glm(as.factor(sex) ~ as.factor(reg), family = binomial,  data = df)
summary(sex.glm)

memAcc.lm = lm(memAcc ~ as.factor(reg), data = df)
summary(memAcc.lm)

memD.lm = lm(memD ~ as.factor(reg), data = df)
summary(memD.lm)


```

## summarize table

```{r table}

df %>% group_by(reg) %>% summarize(N = n(), 
                                   Fem = sum(sex == "F"),
                                   agemean = mean(age), 
                                   agesd = sd(age),
                                   memAccmean = mean(memAcc),  
                                   memAccsd = sd(memAcc),
                                   memDmean = mean(memD), 
                                   memDsd = sd(memD),
                                   encHitmean = mean(encHIT),
                                   encHitsd = sd(encHIT),
                                   encMissmean = mean(encMISS),
                                   encMisssd = sd(encMISS),
                                   retHitmean = mean(retHIT),
                                   retHitsd = sd(retHIT),
                                   retMissmean = mean(retMISS),
                                   retMisssd = sd(retMISS) )

```
## models for hit trials only ENCODING 

```{r hit models}

#CHARACTERISTIC PATH LENGTH HIT TRIALS ENCODING
charModel <- lmer(Char ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'enc', hitMiss == 'hit'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")

#STRENGTH HIT TRIALS ENCODING
charModel <- lmer(ST ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'enc', hitMiss == 'hit'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")


#SATURATION HIT TRIALS ENCODING
charModel <- lmer(Saturation ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'enc', hitMiss == 'hit'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")


```

## models for miss trials only ENCODING 

```{r miss models}

#CHARACTERISTIC PATH LENGTH HIT TRIALS ENCODING
charModel <- lmer(Char ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'enc', hitMiss == 'miss'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")

#STRENGTH HIT TRIALS ENCODING
charModel <- lmer(ST ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'enc', hitMiss == 'miss'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")


#SATURATION HIT TRIALS ENCODING
charModel <- lmer(Saturation ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'enc', hitMiss == 'miss'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")


```


## models for hit trials only RETRIEVAL 

```{r hit models ret}

#CHARACTERISTIC PATH LENGTH HIT TRIALS ENCODING
charModel <- lmer(Char ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'ret', hitMiss == 'hit'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")

#STRENGTH HIT TRIALS ENCODING
charModel <- lmer(ST ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'ret', hitMiss == 'hit'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")


#SATURATION HIT TRIALS ENCODING
charModel <- lmer(Saturation ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'ret', hitMiss == 'hit'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")


```

## models for miss trials only RETRIEVAL 

```{r miss models ret}

#CHARACTERISTIC PATH LENGTH HIT TRIALS ENCODING
charModel <- lmer(Char ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'ret', hitMiss == 'miss'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")

#STRENGTH HIT TRIALS ENCODING
charModel <- lmer(ST ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'ret', hitMiss == 'miss'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")


#SATURATION HIT TRIALS ENCODING
charModel <- lmer(Saturation ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'ret', hitMiss == 'miss'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")


```


## characteristic mean vector length retrieval 

```{r char retrieve}
reg_order <- c("hip", "mtl", "acc", "dlPFC", "pPFC")
# Color data frame in R
regColors <- data.frame(
  parahip = rgb(214, 77, 97, maxColorValue = 255),       # dark pink
  dlPFC = rgb(145, 162, 80, maxColorValue = 255),        # light forest green
  iTemp = rgb(145, 162, 80, maxColorValue = 255),        # light forest green
  lTemp = rgb(145, 162, 80, maxColorValue = 255),        # light forest green
  polarPFC = rgb(51, 102, 153, maxColorValue = 255),     # lilac
  visual = rgb(132, 125, 212, maxColorValue = 255),      # lilac
  ACC = rgb(204, 153, 204, maxColorValue = 255),         # dark red
  PCC = rgb(184, 78, 83, maxColorValue = 255),          # dark red
  Hip = rgb(61, 187, 218, maxColorValue = 255)           # dusky blue
)

long_df$reg1 = factor(long_df$reg1, reg_order)


#region by region? hip: 
charModel <- lmer(Char ~  reg1 * timeSet * hitMiss + (1|realID) + (1|realID2), 
                     data = filter(long_df, encRet == 'ret' ), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

charModel <- lmer(Char ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'ret', hitMiss == 'hit'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")

em_dat_all_adj <- emmeans(charModel, pairwise ~ reg1*timeSet , type="response", adjust = "holm")
emm <- emmeans(glm_test_all_adj, ~ reg1*timeSet)
em_dat_all_adj

plot(em_dat_all_adj)
em_dat_all_adj = as.data.frame(em_dat_all_adj)


charModel <- lmer(Char ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'ret', hitMiss == 'miss'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emm <- emmeans(charModel, ~ reg1 * timeSet)
pairs(emm, by = c("reg1"), adjust = "holm")



long_df %>% filter(encRet == 'ret', hitMiss == 'hit') %>%
  ggplot(aes( fill = timeSet, color = timeSet, y = Char, x = reg1)) + 
    geom_boxplot(outlier.shape = NA, alpha = .75, 
                 position = position_dodge(.85)) +
    geom_jitter(show.legend = F, shape = 21, size = 4, alpha = .5,
                position = position_jitterdodge(dodge.width = .85, 
                                                jitter.width = .2)) + 
    scale_fill_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
    scale_color_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
  theme_classic() +
  ylim(c(0,50)) + 
    theme(axis.line = element_line(color = 'black', linewidth = 3),
          axis.ticks = element_line(colour = "black", linewidth = 2),
          axis.ticks.length=unit(-.25, "cm"),
          text = element_text(size = 20),
          legend.position = 'none',
          axis.text.x = element_text(margin = margin(t = 10)),
          axis.text.y = element_text(margin = margin(r = 10))) 


  
long_df %>% filter(encRet == 'enc', hitMiss == 'miss') %>%
  ggplot(aes( fill = timeSet, color = timeSet, y = Char, x = reg1)) + 
    geom_boxplot(outlier.shape = NA, alpha = .75, 
                 position = position_dodge(.85)) +
    geom_jitter(show.legend = F, shape = 21, size = 4, alpha = .2,
                position = position_jitterdodge(dodge.width = .85, 
                                                jitter.width = .2)) + 
    scale_fill_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
    scale_color_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
  theme_classic() +
  ylim(c(0,50)) + 
    theme(axis.line = element_line(color = 'black', linewidth = 3),
          axis.ticks = element_line(colour = "black", linewidth = 2),
          axis.ticks.length=unit(-.25, "cm"),
          text = element_text(size = 20),
          legend.position = 'none',
          axis.text.x = element_text(margin = margin(t = 10)),
          axis.text.y = element_text(margin = margin(r = 10)))  


```

## encoding strength mean vector length

```{r strength encode}

reg_order <- c("hip", "mtl", "acc", "dlPFC", "pPFC")
# Color data frame in R
regColors <- data.frame(
  parahip = rgb(214, 77, 97, maxColorValue = 255),       # dark pink
  dlPFC = rgb(145, 162, 80, maxColorValue = 255),        # light forest green
  iTemp = rgb(145, 162, 80, maxColorValue = 255),        # light forest green
  lTemp = rgb(145, 162, 80, maxColorValue = 255),        # light forest green
  polarPFC = rgb(51, 102, 153, maxColorValue = 255),     # lilac
  visual = rgb(132, 125, 212, maxColorValue = 255),      # lilac
  ACC = rgb(204, 153, 204, maxColorValue = 255),         # dark red
  PCC = rgb(184, 78, 83, maxColorValue = 255),          # dark red
  Hip = rgb(61, 187, 218, maxColorValue = 255)           # dusky blue
)

long_df$reg1 = factor(long_df$reg1, reg_order)


#region by region? hip: 
charModel <- lmer(ST ~  reg1 * timeSet * hitMiss + (1|realID), 
                     data = filter(long_df, encRet == 'enc'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

charModel <- lmer(ST ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'enc', hitMiss == 'hit'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emmeans(charModel, pairwise ~ reg1 * timeSet , type="response", adjust = "holm")

charModel <- lmer(ST ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'enc', hitMiss == 'miss'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emmeans(charModel, pairwise ~ reg1 * timeSet , type="response", adjust = "holm")




long_df %>% filter(encRet == 'enc', hitMiss == 'hit') %>%
  ggplot(aes( fill = timeSet, color = timeSet, y = ST, x = reg1)) + 
    geom_boxplot(outlier.shape = NA, alpha = .75, 
                 position = position_dodge(.85)) +
    geom_jitter(show.legend = F, shape = 21, size = 4, 
                position = position_jitterdodge(dodge.width = .85, 
                                                jitter.width = .2)) + 
    scale_fill_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
    scale_color_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
  theme_classic() +
  ylim(c(0,.2)) + 
    theme(axis.line = element_line(color = 'black', linewidth = 3),
          axis.ticks = element_line(colour = "black", linewidth = 2),
          axis.ticks.length=unit(-.25, "cm"),
          text = element_text(size = 20),
          legend.position = 'none',
          axis.text.x = element_text(margin = margin(t = 10)),
          axis.text.y = element_text(margin = margin(r = 10))) 


  
long_df %>% filter(encRet == 'enc', hitMiss == 'miss') %>%
  ggplot(aes( fill = timeSet, color = timeSet, y = ST, x = reg1)) + 
    geom_boxplot(outlier.shape = NA, alpha = .75, 
                 position = position_dodge(.85)) +
    geom_jitter(show.legend = F, shape = 21, size = 4, 
                position = position_jitterdodge(dodge.width = .85, 
                                                jitter.width = .2)) + 
    scale_fill_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
    scale_color_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
  theme_classic() +
  ylim(c(0,.2)) + 
    theme(axis.line = element_line(color = 'black', linewidth = 3),
          axis.ticks = element_line(colour = "black", linewidth = 2),
          axis.ticks.length=unit(-.25, "cm"),
          text = element_text(size = 20),
          legend.position = 'none',
          axis.text.x = element_text(margin = margin(t = 10)),
          axis.text.y = element_text(margin = margin(r = 10))) 

```
## characteristic mean vector length retrieval 

```{r char retrieve}
reg_order <- c("hip", "mtl", "acc", "dlPFC", "pPFC")
# Color data frame in R
regColors <- data.frame(
  parahip = rgb(214, 77, 97, maxColorValue = 255),       # dark pink
  dlPFC = rgb(145, 162, 80, maxColorValue = 255),        # light forest green
  iTemp = rgb(145, 162, 80, maxColorValue = 255),        # light forest green
  lTemp = rgb(145, 162, 80, maxColorValue = 255),        # light forest green
  polarPFC = rgb(51, 102, 153, maxColorValue = 255),     # lilac
  visual = rgb(132, 125, 212, maxColorValue = 255),      # lilac
  ACC = rgb(204, 153, 204, maxColorValue = 255),         # dark red
  PCC = rgb(184, 78, 83, maxColorValue = 255),          # dark red
  Hip = rgb(61, 187, 218, maxColorValue = 255)           # dusky blue
)

long_df$reg1 = factor(long_df$reg1, reg_order)


#region by region? hip: 
charModel <- lmer(Char ~  reg1 * timeSet * hitMiss + (1|realID), 
                     data = filter(long_df, encRet == 'ret'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

charModel <- lmer(Char ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'ret', hitMiss == 'hit'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emmeans(charModel, pairwise ~ reg1 * timeSet , type="response", adjust = "holm")

charModel <- lmer(Char ~  reg1 * timeSet + (1|realID), 
                     data = filter(long_df, encRet == 'ret', hitMiss == 'miss'), 
            control = lmerControl(optimizer = "bobyqa"))
summary(charModel)
Anova(charModel)

emmeans(charModel, pairwise ~ reg1 * timeSet , type="response", adjust = "holm")



long_df %>% filter(encRet == 'ret', hitMiss == 'hit') %>%
  ggplot(aes( fill = timeSet, color = timeSet, y = Char, x = reg1)) + 
    geom_boxplot(outlier.shape = NA, alpha = .75, 
                 position = position_dodge(.85)) +
    geom_jitter(show.legend = F, shape = 21, size = 4, 
                position = position_jitterdodge(dodge.width = .85, 
                                                jitter.width = .2)) + 
    scale_fill_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
    scale_color_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
  theme_classic() +
  ylim(c(0,50)) + 
    theme(axis.line = element_line(color = 'black', linewidth = 3),
          axis.ticks = element_line(colour = "black", linewidth = 2),
          axis.ticks.length=unit(-.25, "cm"),
          text = element_text(size = 20),
          legend.position = 'none',
          axis.text.x = element_text(margin = margin(t = 10)),
          axis.text.y = element_text(margin = margin(r = 10))) 


  
long_df %>% filter(encRet == 'ret', hitMiss == 'miss') %>%
  ggplot(aes( fill = timeSet, color = timeSet, y = Char, x = reg1)) + 
    geom_boxplot(outlier.shape = NA, alpha = .75, 
                 position = position_dodge(.85)) +
    geom_jitter(show.legend = F, shape = 21, size = 4, 
                position = position_jitterdodge(dodge.width = .85, 
                                                jitter.width = .2)) + 
    scale_fill_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
    scale_color_manual(values=c( "#E1C271", "#3BACDD"),
                      labels=c(  'HFB', 'Image')) +  
  theme_classic() +
  ylim(c(0,50)) + 
    theme(axis.line = element_line(color = 'black', linewidth = 3),
          axis.ticks = element_line(colour = "black", linewidth = 2),
          axis.ticks.length=unit(-.25, "cm"),
          text = element_text(size = 20),
          legend.position = 'none',
          axis.text.x = element_text(margin = margin(t = 10)),
          axis.text.y = element_text(margin = margin(r = 10))) 


```



